---
title: "French given names per year per department"
author: "Lucas Mello Schnorr, Jean-Marc Vincent"
date: "October, 2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# The environment
library(tidyverse)
library(ggplot2)
```
The aim of the activity is to develop a methodology to answer a specific question on a given dataset. 

The dataset is the set of Firstname given in France on a large period of time. 
[given names data set of INSEE](https://www.insee.fr/fr/statistiques/fichier/2540004), we choose this dataset because it is sufficiently large, you can't do the analysis by hand, the structure is simple


You need to use the _tidyverse_ for this analysis. Unzip the file _dpt2019_txt.zip_ (to get the **dpt2019.csv**). Read in R with this code. Note that you might need to install the `readr` package with the appropriate command.

## Download Raw Data from the website
```{r}
file = "dpt2020_txt.zip"
if(!file.exists(file)){
  download.file("https://www.insee.fr/fr/statistiques/fichier/2540004/dpt2020_csv.zip",
	destfile=file)
}
unzip(file)
```

## Build the Dataframe from file
```{r}
data <- read_delim("dpt2020.csv", delim =";")
```
Translation in english of variables names: 
sexe -> gender 
preusuel (prénom usuel) -> Firstname
annais (année de naissance) -> Birth year
dpt (département) -> department (administrative area unit)
nombre -> number

All of these following questions may need a preliminary analysis of the data, feel free to present answers and justifications in your own order and structure your report as it should be for a scientific report.

1. Choose a firstname and analyse its frequency along time. Compare several firstnames frequency
2. Establish, by gender, the most given firstname by year. 
3. Make a short synthesis
4. Advanced (not mandatory) : is the firstname correlated with the localization (department) ? What could be a method to analyze such a correlation.

The report should be a pdf knitted from a  notebook (around  3 pages including figures), the notebook and the report should be delivered.

#Solution Proposal
## 1. Choose a firstname and analyse its frequency along time. Compare several firstname's frequency

```{r}
names = c("VANESSA", "PIERRICK", "LOUISETTE", "LOUISA", "MYLA", "ROMANE")
random_data = filter(data, preusuel %in% names & annais != "XXXX")
random_data = random_data %>% group_by(preusuel, annais) %>% 
  summarize(count=sum(nombre), .groups = 'drop') %>% 
  ungroup()
random_data$annais = as.numeric(random_data$annais)
ggplot(random_data, aes(annais, count, colour = preusuel)) + 
  geom_line() 
```

## Note: For the next treatments that will be applied on the data, we will apply the following pre-treatments:
* remove the samples containing 'PRENOMS_RARES' as the firstname.
* delete all the samples with the corresponding year symbolized as 'XXXX'

## 2. Establish, by gender, the most given firstname by year. 

```{r}
filtered_data = filter(data, preusuel != "_PRENOMS_RARES")
filtered_data = filter(filtered_data, annais != "XXXX")
filtered_data$annais = as.numeric(filtered_data$annais)
male = filter(filtered_data, sexe == 1)
female = filter(filtered_data, sexe == 2)
```

```{r}
male_data_plot = male %>% group_by(annais, preusuel) %>% 
  summarise(count=sum(nombre), .groups='drop') %>% 
  group_by(annais) %>% 
  filter(count == max(count)) %>% 
  ungroup()
male_data_plot = tail(male_data_plot, n=20)
```

```{r}
female_data_plot = female %>% group_by(annais, preusuel) %>% 
  summarise(count=sum(nombre), .groups='drop') %>% 
  group_by(annais) %>% 
  filter(count == max(count)) %>% 
  ungroup()
female_data_plot = tail(female_data_plot, n=20)
```

```{r}
ggplot(female_data_plot, aes(annais, count, fill=preusuel)) + geom_bar(stat="identity") + xlab("Year") + ylab("Appearance Frequency")
```

```{r}
ggplot(male_data_plot, aes(annais, count, fill=preusuel)) + 
  geom_bar(stat="identity") + 
  xlab("Year") + 
  ylab("Appearance Frequency")
```

## 3. Make a short analysis
These are the points of our analysis.

* There samples with **_PRENOMS_RARES** were not probably significant at the time of the registration but once accumulated they represent a considerable amount of unknown data.
* Similarly, the attribute **year** faces the same problem and the joint deletion of these unknown attributes lead to drastic scale down in the amount of the data available for the treatment.